---
title: "HOMEWORK 3 - Creating Value Through Data Mining (S402010)"
author: "Liam Phan"
date: "`r Sys.Date()`"
output:
  rmdformats::material :
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: true
    highlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning=FALSE, comment=FALSE, message=FALSE,results="asis")

```



# <span style="color: #1c6155;">Quick Start</span> 

> Most of the plots are interactive, you can click or zoom to get more details ! Also don't hesitate to click on plots, they will zoom automatically ! 

## Loading Packages

```{r 1, warning=FALSE, message=FALSE }

library(data.table) # Efficient Dataframe 
library(lubridate) # For Dates 
library(tidyverse) # Multiple Package for Useful Data wrangling
library(esquisse) # Intuitive plotting
library(plyr) # Data splitting
library(dplyr) # Data Wrangling
library(ggplot2) # Plot Graphs
library(naniar) # for NA exploration in Dataframe
library(plotly) # Make ggplot2 Dynamic
library(gridExtra) # Multiple Plot at once
library(RColorBrewer) # For Color Palette
library(rmdformats) # Theme of HTML
library(flextable) # Show Table
library(class) # K-NN
library(summarytools) # Beautiful and Efficient Summary for Dataset
library(pivottabler) # Pivot Table
library(naivebayes) # Naive Bayes Function
library(caret) # Confusion Matrix

```



# <span style="color: #1c6155;">Dataset Preparation</span> 

```{r clean environment, include=FALSE}

# Clean Environment
rm(list = ls()) 

```

## Loading the dataset called "ToyotaCorolla.csv"

```{r loading dataset}

# Load the Dataset with Fread()
ToyotaDT <- fread("DATA/ToyotaCorolla.csv")

```


## Quick Preview

```{r preview of dataset}

# Preview of the Dataset
flextable(head(ToyotaDT,2)) %>% fontsize(size = 8, part = "all")

```




> Dataset Description: The file ToyotaCorolla.csv contains data on used cars on sale during late summer of 2004 in the Netherlands. It has 1436 records containing detail on 38 attributes, including Price, Age, Kilometers, HP (Horse Power), and other specifications.


```{r summary of dataset}

dfSummary(ToyotaDT, 
          plain.ascii  = FALSE, 
          style        = "grid", 
          graph.magnif = 0.75, 
          valid.col    = FALSE,
          tmp.img.dir  = "/tmp")

```

## Missing Variables Plot

<center>

```{r 2222, echo=FALSE}

# Missing Variables Plot for the Dataset
gg_miss_var(ToyotaDT, show_pct = TRUE)

```

</center>

> We can see that there is no missing values in our dataset ToyotaCorolla.csv


# <span style="color: #1c6155;">Ex 6.4</span> 


# <span style="color: #1c6155;">Ex 9.3</span> 

# <span style="color: #1c6155;">Ex 11.3</span> 


# <span style="color: #1c6155;">References</span>

[Github Repo for this Homework 3](https://github.com/LiamPhan17/DATA_MINING_HW3)

[Data Mining for Business Analytics: Concepts, Techniques, and Applications in R](https://www.wiley.com/en-us/Data+Mining+for+Business+Analytics:+Concepts,+Techniques,+and+Applications+in+R-p-9781118879368)

[Summarytools in R Markdown Documents](https://cran.r-project.org/web/packages/summarytools/vignettes/rmarkdown.html)

